### 2016-04-07 Projects/DelCo_2012/Report/DelCo_2012.tex
clean up temp data in fire supression section

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results}\label{tab:Test_Results_2}
\begin{tabular}{lccc}
\toprule[1.5pt]
                     & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	             & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 1~m (3~ft) Above Floor \\
\midrule
CAF~7 Stairell       & 579~$^{\circ}$C - 258~$^{\circ}$C   & 487~$^{\circ}$C - 193~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7 Stairwell    & 514~$^{\circ}$C - 260~$^{\circ}$C   & 454~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a Stairwell     & 474~$^{\circ}$C - 283~$^{\circ}$C   & 422~$^{\circ}$C - 249~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b Stairwell     & 452~$^{\circ}$C - 238~$^{\circ}$C   & 388~$^{\circ}$C - 189~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Class A~1 Stairwell  & 441~$^{\circ}$C - 304~$^{\circ}$C   & 258~$^{\circ}$C - 234~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a Stairwell     & 468~$^{\circ}$C - 270~$^{\circ}$C   & 418~$^{\circ}$C - 234~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b Stairwell     & 508~$^{\circ}$C - 336~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

>>>>

\begin{table}[!ht]
\centering
\caption{Fire Suppression Results}\label{tab:Test_Results_2}
\begin{tabular}{lccc}
\toprule[1.5pt]
                     & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
Test 	             & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 1~m (3~ft) Above Floor \\
\midrule
CAF~7 Stairell       & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
Water~7 Stairwell    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
CAF~8a Stairwell     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
CAF~8b Stairwell     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
Class A~1 Stairwell  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
CAF~9a Stairwell     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
CAF~9b Stairwell     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}
